PyPy's Approach to Virtual Machine Construction

### 2006-07-12 talk/dls2006/paper.tex
simple fixes from the reviews

When the translation target is C or C-like environments, the first of
the transformation steps takes the RPython-typed flow graphs, still
containing polymorphic operations only, and produces flow graphs with
monomorphic C-like operations and C-like types.  In the simplest case,
this is the only transformation step: these graphs are directly fed to
the C back-end, which turns them into ANSI C source code.

@@

The worst case behaviors that can appear in the model described above
involve the lattice of Pbcs, involving variables that could contain
e.g.\ one function object among many.  An example of such behavior is
code manipulating a table of function objects: when an item is read
out of the table, its type is a large Pbc set: $Pbc(\{f_1, f_2, f_3,
\ldots\})$.  But in this example, the whole set is available at once,
and not built incrementally by successive discoveries.  This seems to
be often the case in practice: it is not very common for programs to
manipulate objects that belong to a large but finite family -- and when
they do, the whole family tends to be available early on, requiring
few reflowing.

>>>>

When the translation target is C or C-like environments, the first of
the transformation steps takes the RPython-typed flow graphs, still
containing polymorphic operations only, and produces flow graphs with
monomorphic C-like operations and C-like types.  In the simplest case,
this is the only transformation step: these graphs are directly fed to
the C emitting back-end, which turns them into ANSI C source code.

@@

The worst case behaviors that can appear in the model described above
involve the lattice of Pbcs, involving variables that could contain
e.g.\ one function object among many.  An example of such behavior is
code manipulating a table of function objects: when an item is read
out of the table, its type is a large Pbc set: $Pbc(\{f_1, f_2, f_3,
\ldots\})$.  But in this example, the whole set is available at once,
and not built incrementally by successive discoveries.  This seems to
be often the case in practice: it is not very common for programs to
manipulate objects that belong to a large but finite family -- and when
they do, the whole family tends to be available early on, requiring
few reflowings.
